Rapid cycleway prioritisation tool

### 2020-06-01 code/index.Rmd
Change name of Key cycle routes to Cohesive network
see #55 for context

command to make these changes:

sd 'Key cycle routes' 'Cohesive network' README.Rmd
README.md
README_files
article.R
article.Rmd
cities/birmingham.Rmd
cities/bristol.Rmd
cities/cambridge.Rmd
cities/leeds.Rmd
cities/leicester.Rmd
cities/liverpool.Rmd
cities/london.Rmd
cities/manchester.Rmd
cities/newcastle.Rmd
cities/sheffield.Rmd
code/article-methods-1.R
code/article-methods-cambridge-test.R
code/boundaries.R
code/boundaries2.R
code/build.R
code/build.R.orig
code/build.Rmd
code/build.spin.R
code/build.spin.Rmd
code/builda

The aim of this tool is to help reveal the locations that have the greatest potential for new cycleways. It should be used together with local knowledge, to prioritise where to install rapid measures to support safe travel as part of the COVID-19 response. We anticipate that this may be used in the development of a range of temporary, experimental and longer term measures to make the streets safer for us all, as new travel patterns and behaviours emerge in the coming weeks and months.

@@

We have focused on roads which are sufficiently wide that part of the road space could potentially be reallocated to provide additional space for active transport without preventing traffic movement. In identifying these locations, we have not taken average traffic volumes into account. The pandemic has had a severe impact on movement and traffic flows are currently below normal levels. Instead, we simply identify streets that have multiple vehicle lanes or a carriageway width of greater than 10m.

@@

@@

- Type in the name of the local authority of interest into the search bar above the table below and click on the associated URL.
- Explore the results in the map (you will find a link to a full screen map) and the table of 'top roads' which can be ranked in various ways with reference to descriptions of the map layers described below.
- Interpret the results with care based on other sources of information and an understanding of the limitations of the analysis (see 'Known issues and limitations' below).

@@

## 3. Spare lane(s)

@@

```{r}
dn = "popupCycleways/v0.3" # dirctory name
built_regions = list.files(dn)
regions = regions %>% 
  filter(stringr::str_detect(string = Name, "Scilly", negate = TRUE))
regions %>%
  sf::st_drop_geometry() %>%
  filter(html_name %in% built_regions) 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```

>>>>

This tool helps identify road sections for road space reallocation and other interventions to create new cycleways.
Used with local knowledge, it provides a strong evidence base to support planning of rapid measures to support safe travel as part of the COVID-19 response.
The evidence may be used to support a range of temporary, experimental and permanent treatments that will enable shift to walking and cycling in the coming weeks and months, to help overcome capacity constraints on public transport modes and prevent gridlock as the lockdown eases.

@@

The focus is on roads the either have a spare lane or that have an estimated width of above 10 m, *and* high cycling potential.
The 10 m width is an indicator of road conditions and larger widths, of 15+ m, may be required for road space reallocation without other changes such as making roads one way for motor traffic or removing central markings as described in , depending on factors such as on street parking levels.
The work is based evidence that road space can be reallocated without causing congestion at a time when traffic levels, particularly during the rush hours, are greatly reduced.

@@

# How to use the tool

@@

- Type in the name of the local authority of interest into the search bar above the table below and click on the associated URL.
- Explore the results in the map (you will find a link to a full screen map) by panning, zooming and clicking on the layers. See additional layers by clicking on the layers icon in the top left of the map.
- Rank the 'top roads' in various ways (including by length and cycling potential) to support prioritisation of road space reallocation schemes.
- Interpret the results with care based on other sources of information and an understanding of the limitations of the analysis (see 'Known issues and limitations' below).
- Refer to the description of the map layers below when exploring the results and complete the [web form](https://urldefense.proofpoint.com/v2/url?u=https-3A__forms.office.com_Pages_ResponsePage.aspx-3Fid-3DqO3qvR3IzkWGPlIypTW3y9orQ9urif9IgBaXiRS9eEpUM0JCTDRFTTEwSDRVMUs0VVhVWEdGRDA3RS4u&d=DwMCaQ&c=troKkvwivNn_CddsvWCHHPiPoFoTgTGIbXJULvYU158&r=DXeEYtdSYDBZN2DBwEgAHMmX5PQ_ob9r2MynFWta2mU&m=mkyUa3RIC9d5LSrHUqk_WdstQR1OQuTWyYLBecHFMm0&s=dD7GVcQbjZ2AcdCObSe-rNKmLLDBhu98ChFupIIrlJA&e=) with any feedback.

@@

## 3. Spare lane(s) (not shown be default)

@@

```{r}
dn = "popupCycleways/v0.3" # dirctory name
built_regions = list.files(dn)
regions = regions %>% 
  filter(stringr::str_detect(string = Name, "Scilly", negate = TRUE))
regions %>%
  sf::st_drop_geometry() %>%
  filter(html_name %in% built_regions) %>% 
  select(Name, Level, url) %>% 
  arrange(Name) %>% 
  DT::datatable(escape = -4)
```
